\Large Exponential Random Graph Models with Big Networks: Maximum Pseudolikelihood Estimation and the\\Parametric Bootstrap

### 2017-03-13 TeX/paper.tex
started intro paragraph

 Coming soon...

>>>>

The field of network science faces a double-edge sword when it comes to computational limitations to innovation. First, the networks under study are growing larger with each year. {\bf [CHRISTIAN, WOULD YOU CHECK OUT N NODES IN {\em SOCIAL NETWORKS}?]}. Second, analytical methods are growing more sophisticated, increasingly involving estimation and optimization, going beyond descriptive calculations {\bf [Could also classify articles based on whether a statistical model is used {\em SOCIAL NETWORKS}?]}. In order to avoid a limiting horizon in which state-of-the-art methods cannot be used with state-of-the-art ``big'' data, network methodologists need to consider all available options in easing the computational burden of tools for network analysis.
